Ms 1

### 2018-01-19 ms1/ms1_display.Rmd
small updates

claims_by_abx %>%
  mutate(panel = factor(case_when(
    .$abx %in% c('pde', 'pde_approp', 'pde_inapprop', 'pde_nodx') ~ 1,
    .$abx %in% c('azithromycin', 'ciprofloxacin', 'amoxicillin', 'cephalexin', 'tmpsmx', 'levofloxacin') ~ 2,
    .$abx %in% c('amoxclav', 'doxycycline', 'nitrofurantoin', 'clindamycin') ~ 3
  ))) %>%
  mutate(abx=case_when(
    .$abx == 'pde' ~ 'Overall use',
    .$abx == 'pde_inapprop' ~ 'Inappropriate use',
    .$abx == 'pde_approp' ~ 'Appropriate use',
    .$abx == 'pde_nodx' ~ 'Indeterminate use',
    .$abx == 'amoxclav' ~ 'amox/clav',
    .$abx == 'tmpsmx' ~ 'TMP/SMX',
    TRUE ~ .$abx)
  ) %>%
  arrange(year, desc(cpkp)) %>%
  {
  ggplot(., aes(x=year, y=cpkp, group=abx)) +
  geom_blank(data=dummy) +
  geom_line() +
  geom_text_repel(
    data=filter(., year==2013),
    aes(label=abx)
  ) +
  facet_wrap(~panel, scales='free_y', labeller=labeller(panel=panel_labels)) +
  theme_classic() +
  theme(panel.grid.minor.x=element_blank(),
        strip.background = element_blank()) +
  scale_x_continuous(expand=c(0, 0), name='') +
  scale_y_continuous(expand=c(0, 0), name='claims per 1,000 beneficiaries per year')
  }

@@

abx_trends %>%
  mutate(antibiotic=case_when(
    .$antibiotic == 'n_pde' ~ 'Overall use',
    .$antibiotic == 'n_pde_inapprop' ~ 'Inappropriate use',
    .$antibiotic == 'n_pde_approp' ~ 'Appropriate use',
    .$antibiotic == 'n_pde_nodx' ~ 'Indeterminate use',
    .$antibiotic == 'amoxclav' ~ 'amox/clav',
    .$antibiotic == 'tmpsmx' ~ 'TMP/SMX',
    TRUE ~ .$antibiotic)
  ) %>%
  # put the abx in order
  arrange(desc(estimate)) %>%
  mutate(antibiotic=fct_inorder(factor(antibiotic))) %>%
  mutate(antibiotic=fct_relevel(antibiotic, c('Overall use', 'Inappropriate use', 'Appropriate use', 'Indeterminate use'))) %>%
  mutate(antibiotic=fct_rev(antibiotic)) %>%
  # plot
  ggplot(aes(x=antibiotic, y=estimate, ymin=lower_ci, ymax=upper_ci)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in claims per beneficiary per year from 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 33), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=12),
        axis.text = element_text(size=12))

@@

```{r inappropriate_fraction}
claims_by_abx %>%
  filter(str_detect(abx, '^pde')) %>%
  select(year, abx, n) %>%
  spread(abx, n) %>%
  mutate_at(vars(matches('^pde_')), function(x) round(x / .$pde * 100, 1)) %>%
  select(-pde) %>%
  kable(caption='Proportion of app., inapp., and no-dx prescribing')
```

@@

```{r claims_by_demography}
subpop_table = read_tsv('tables/new/claims_by_subpop.tsv') %>%
  mutate(cpkp=round(n_pde/n_bene*1000)) %>%
  filter(year %in% c(2011, 2014)) %>%
  select(subpop, year, cpkp) %>%
  spread(year, cpkp)

>>>>

claims_by_abx %>%
  mutate(panel = factor(case_when(
    .$abx %in% c('pde', 'pde_approp', 'pde_inapprop', 'pde_nodx') ~ 1,
    .$abx %in% c('azithromycin', 'ciprofloxacin', 'amoxicillin', 'cephalexin', 'tmpsmx', 'levofloxacin') ~ 2,
    .$abx %in% c('amoxclav', 'doxycycline', 'nitrofurantoin', 'clindamycin') ~ 3
  ))) %>%
  filter(!is.na(panel)) %>% # remove metro
  mutate(abx=case_when(
    .$abx == 'pde' ~ 'Overall use',
    .$abx == 'pde_inapprop' ~ 'Inappropriate use',
    .$abx == 'pde_approp' ~ 'Appropriate use',
    .$abx == 'pde_nodx' ~ 'Indeterminate use',
    .$abx == 'amoxclav' ~ 'amox/clav',
    .$abx == 'tmpsmx' ~ 'TMP/SMX',
    TRUE ~ .$abx)
  ) %>%
  arrange(year, desc(cpkp)) %>%
  {
  ggplot(., aes(x=year, y=cpkp, group=abx)) +
  geom_blank(data=dummy) +
  geom_line() +
  geom_text_repel(
    data=filter(., year==2013),
    aes(label=abx)
  ) +
  facet_wrap(~panel, scales='free_y', labeller=labeller(panel=panel_labels)) +
  theme_classic() +
  theme(panel.grid.minor.x=element_blank(),
        strip.background = element_blank()) +
  scale_x_continuous(expand=c(0, 0), name='') +
  scale_y_continuous(expand=c(0, 0), name='claims per 1,000 beneficiaries per year')
  }

@@

abx_trends %>%
  filter(antibiotic != 'metronidazole') %>%
  mutate(antibiotic=case_when(
    .$antibiotic == 'n_pde' ~ 'Overall use',
    .$antibiotic == 'n_pde_inapprop' ~ 'Inappropriate use',
    .$antibiotic == 'n_pde_approp' ~ 'Appropriate use',
    .$antibiotic == 'n_pde_nodx' ~ 'Indeterminate use',
    .$antibiotic == 'amoxclav' ~ 'amox/clav',
    .$antibiotic == 'tmpsmx' ~ 'TMP/SMX',
    TRUE ~ .$antibiotic)
  ) %>%
  # put the abx in order
  arrange(desc(estimate)) %>%
  mutate(antibiotic=fct_inorder(factor(antibiotic))) %>%
  mutate(antibiotic=fct_relevel(antibiotic, c('Overall use', 'Inappropriate use', 'Appropriate use', 'Indeterminate use'))) %>%
  mutate(antibiotic=fct_rev(antibiotic)) %>%
  # plot
  ggplot(aes(x=antibiotic, y=estimate, ymin=lower_ci, ymax=upper_ci)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in claims per beneficiary per year from 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 33), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=12),
        axis.text = element_text(size=12))

@@

```{r inappropriate_fraction}
claims_by_abx %>%
  filter(str_detect(abx, '^pde')) %>%
  select(year, abx, n) %>%
  spread(abx, n) %>%
  mutate(denom=pde_approp + pde_inapprop + pde_nodx) %>%
  mutate_at(vars(matches('^pde_')), function(x) round(x / .$denom * 100, 1)) %>%
  select(-pde, -denom) %>%
  kable(caption='Proportion of app., inapp., and no-dx prescribing')
```

@@

```{r claims_by_demography}
subpop_table = read_tsv('tables/new/claims_by_subpop.tsv') %>%
  mutate(cpkp=round(n_pde/n_bene*1000)) %>%
  #filter(year %in% c(2011, 2014)) %>%
  select(subpop, year, cpkp) %>%
  spread(year, cpkp)
